Typed Functional Genetic Programming

### 2013-07-08 tex/thesis.tex
[tex]

\subsection{Reductions for $c \in C$}
\textbf{TODO možná vynechat...}

@@

@@

	\begin{align*}
	\alpha      \in A          &\Rightarrow     \alpha   \in \mathbb{T} \\
	\sigma,\tau \in \mathbb{T} &\Rightarrow ( \sigma \rightarrow  \tau ) \in \mathbb{T} 
	\end{align*}

\textbf{TODO} 
\begin{itemize}
	\item TALK ABOUT $\tau_1 \rightarrow \dots \rightarrow \tau_n \rightarrow \alpha$ 
	\item TALK ABOUT arrow/parenthesis conventions. 
\end{itemize}

\subsection{Long normal form}
\label{lnf}

\textbf{TODO : promluvit zde o long normal form což propojuje 
		  tuhle sekci se sekcí o barenregt-like 	
		  pravidlech \ref{barlike}.
}

@@

%"Barendregt-like"
\subsection{Inference and grammar rules producing 
terms in Long normal form}
\label{barlike}

As is said in \cite{barendregt10} there are two
inference/grammar rules which together generate
simply typed lambda terms in their long normal forms
(defined in \ref{lnf}).

@@

\chapter{ A mathematical view of the designed system }

>>>>

%\subsection{Reductions for $c \in C$}
%\textbf{TODO možná vynechat...}

@@

\newcommand{\ar}{\rightarrow\xspace}
\newcommand{\T}{\mathbb{T}\xspace}

@@

\begin{align*}
\alpha      \in A  &\then   \alpha \in \T \\
\sigma,\tau \in \T &\then ( \sigma \ar  \tau ) \in \T 
\end{align*}

Type $\sigma \ar \tau$ is type for functions taking as input
something of a type $\sigma$ and returning 
as output something of a type $\tau$. \\

We use following notation
abbreviation for better readability:\\

$\tau_1 \ar \tau_2 \ar \dots \ar \tau_n$ means 
$\tau_1 \ar (\tau_2 \ar (\dots \ar (\tau_{n-1} \ar \tau_n)\dots))$.\\

In other words, the operator $\ar$ is right-associative.\\

It is easy to see that every $\sigma \in \T$ may be expressed as 
$\tau_1 \ar \dots \ar \tau_n \ar \alpha$ 
where $\alpha \in A$ and $n \geq 0$.\footnote{ 
We can prove it by induction on size of $\sigma$. 
For $\sigma = \alpha \in \T$ is $n = 0$ and for $\sigma = \tau_0 \ar \rho$
we have from induction hypothesis that $\rho = \tau_1 \ar \dots \ar \tau_n \ar \alpha$,
therefore
$\sigma = \tau_0 \ar \tau_1 \ar \dots \ar \tau_n \ar \alpha$.}

Technically speaking, we have types only for functions with one argument, but
this property suggests how we can "simulate" function which takes $n$ arguments.

% We will utilize this property ... asi netřeba řikat

~\\
\textbf{TODO} 
\begin{itemize}
	\item určitě promluvit nějak v úvodu k tomu že se jedná o 
	Simply typed lambda kalkulus, zmínit že klasicky se těm alfa z A 
	řiká proměný, ale že je to matoucí vzhledem k polymorfizmu
	\item možná se hlobějc zmínit o curryingu  
\end{itemize}

@@

\section{Long normal form}
\label{lnf}

Let \GMS where $\sigma = \tau_0 \ar \tau_1 \ar \dots \ar \tau_n \ar \alpha$.\\
Then $M$ is in \textit{long normal form} if following 
conditions are satisfied:

\begin{itemize}
 \item $M$ is term of a form $\lam{x_1 \dots x_n}{f~M_1~\dots~M_n}$,
 \item each $M_i$ is in \textit{long normal form}.
\end{itemize}

%"Barendregt-like"
\section{Inference and grammar rules producing 
terms in Long normal form}
\label{barlike}

As is said in \cite{barendregt10} there are two
inference/grammar rules which together generate
simply typed lambda terms in their long normal forms.

@@

\chapter{ Our approach }
